---
title: "WB Farmer Hotline Screening Phone Survey"
author: "Frontieri consultancy"

date: "[Feb 26, 2026 | 08:00 AM]"

output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: fill
    fontsize: 16pt
    
    logo: logo.png

    
---


```{r setup, include=FALSE}
library(flexdashboard)
library(haven)
library(plyr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(highcharter)
library(plotly)
library(DT)
library(stringr)
library(ggplot2)
library(viridis)
library(hrbrthemes)
```
```{r}
#Phone Survey
dataps <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/Eligible_ATI_Farmer_Hotline_phone_survey_500_Callers.dta"
)

dataps <- dataps %>% mutate(across(where(is.labelled), as_factor))

dataps <- dataps %>%
  rename(
    region        = region_preload,
    supervisor_name = supervisor,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

dataps <- dataps %>%
  mutate(
    supervisor_name = str_replace_all(
      supervisor_name,
      c(
        "Shambel Awgachew" = "Shambel",
        "Jemila Umar" = "Jemila",
        "Fikiru Yigezu" = "Fikiru",
        "Gachano Gemechu" = "Gachano",
        "Gashayeneh Deribe" = "Gashayeneh",
        "Misrak Birhanu" = "Misrak"
      )
    )
  )

```

```{r}
#Backcheck Survey
databc <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/Back_Check_Survey_500_Callers_WIDE.dta"
)

databc <- databc %>% mutate(across(where(is.labelled), as_factor))

databc <- databc %>%
  rename(
    region        = region_preload,
    supervisor_name = supervisor,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

databc <- databc %>%
  mutate(
    supervisor_name = str_replace_all(
      supervisor_name,
      c(
        "Shambel Awgachew" = "Shambel",
        "Jemila Umar" = "Jemila",
        "Fikiru Yigezu" = "Fikiru",
        "Gachano Gemechu" = "Gachano",
        "Gashayeneh Deribe" = "Gashayeneh",
        "Misrak Birhanu" = "Misrak"
      )
    )
  )
  
```

```{r}
#Pilot Survey
datapis <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/Pilot_Farmer_Hotline_Screening_Phone_Survey_WIDE.dta"
)

datapis <- datapis %>% mutate(across(where(is.labelled), as_factor))

datapis <- datapis %>%
  rename(
    region        = region_preload,
    enum_name     = enumerator_name,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

datapis <- datapis %>%
  mutate(
    enum_name = str_replace_all(
      enum_name,
      c(
        "Abidulahi mohammed" = "Abidulahi",
        "Addis Worku" = "Addis",
        "Aklilu Zewde Birhane" = "Aklilu",
        "Atakilit Tadesse" = "Atakilit",
        "Bruktawit Molla" = "Bruktawit",
        "Daniel Abebaw" = "Daniel",
        "Eyerus halfom" = "Eyerus",
        "Hilariy Girmay" = "Hilariy",
        "Kabtamu Alemayehu" = "Kabtamu",
        "Kalkidan Wondatir" = "Kalkidan",
        "Mariyam Gudeta" = "Mariyam",
        "Ruth Asfaw" = "Ruth",
        "Shewakena Damitew" = "Shewakena",
        "Sitota G/melak" = "Sitota",
        "Tadele Ejo" = "Tadele",
        "Tena tesfaye" = "Tena",
        "Tirsit Seyoum" = "Tirsit",
        "Tirunesh Ajema" = "Tirunesh",
        "Urgessa Mekonnen" = "Urgessa",
        "Fikadu Thomas" = "Fikadu",
        "Yakob Debela" = "Yakob"
      )
    )
  )

```

ATA PHONE SURVEY
=====================================
Row
-----------------------------------------------------------------------


### TOTAL SYNCED ELIGABLE ATA FARMER HOTLINE PHONE SURVEY INTERVIEWS

```{r}
total_interview<-nrow(dataps)
valueBox(total_interview, icon = "fa-bar-chart")
```

### TOTAL SYNCED ATA BACKCHECK INTERVIEWS

```{r}
total_interview<-nrow(databc)
valueBox(total_interview, icon = "fa-bar-chart")
```

## Column

### NO. OF SYNCED PHONE INTERVIEWS BY SUPERVISORS {data-width="600"}

```{r }
library(dplyr)
library(highcharter)

dataps %>% 
  filter(!is.na(supervisor_name)) %>% 
  count(supervisor_name) %>% 
  arrange(desc(n)) %>% 
  mutate(
    supervisor_name = factor(supervisor_name, levels = supervisor_name),
    name = supervisor_name,
    y = n
  ) %>% 
  hchart(
    type = "column",
    hcaes(x = name, y = y),
    colorByPoint = TRUE
  ) %>%
  hc_title(
    text = "Number of Interviews Synced by Teams",
    style = list(
      fontWeight = "bold",
      fontSize = "22px"
    )
  ) %>%
  hc_xAxis(
    title = list(
      text = "Supervisors",
      style = list(fontWeight = "bold", fontSize = "16px")
    ),
    labels = list(
      rotation = -20,
      style = list(fontWeight = "bold", fontSize = "14px")
    )
  ) %>%
  hc_yAxis(
    title = list(
      text = "Total Interviews Synced",
      style = list(fontWeight = "bold", fontSize = "16px")
    ),
    labels = list(
      style = list(fontWeight = "bold", fontSize = "14px")
    )
  ) %>%
  hc_tooltip(
    style = list(fontSize = "14px"),
    pointFormat = "<b>{point.y}</b> interviews"
  ) %>%
  hc_plotOptions(
    column = list(
      dataLabels = list(
        enabled = TRUE,
        style = list(
          fontWeight = "bold",
          fontSize = "14px"
        ),
        format = "{point.y}"
      ),
      states = list(
        hover = list(brightness = 0.25)
      )
    )
  ) %>%
  hc_legend(enabled = FALSE) %>%
  hc_colors(c(
    "#2ECC71", "#3498DB", "#F1C40F", "#E67E22",
    "#9B59B6", "#1ABC9C", "#E91E63", "#34495E"
  ))
```


### NO. OF SYNCED PHONE SURVEY INTERVIEWS BY SPLIT GROUP {data-width=400}

```{r }
library(dplyr)
library(highcharter)

dataps %>% 
  mutate(
    split_group = recode(
      as.character(split_group),
      "1" = "Group A",
      "2" = "Group B",
      "3" = "Group C"
    )
  ) %>% 
  count(split_group) %>% 
  hchart(
    type = "pie",
    hcaes(
      x = split_group,
      y = n,
      color = split_group
    ),
    colors = group_colors
  ) %>% 
  hc_title(
    text = "Split Group Composition",
    style = list(
      fontWeight = "bold",
      fontSize = "20px"
    )
  ) %>%
  hc_plotOptions(
    pie = list(
      innerSize = "60%",
      dataLabels = list(
        enabled = TRUE,
        useHTML = TRUE,
        style = list(
          fontWeight = "bold",
          fontSize = "14px"
        ),
        format = "<b>{point.name}</b><br>{point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_tooltip(
    useHTML = TRUE,
    style = list(
      fontWeight = "bold",
      fontSize = "14px"
    ),
    pointFormat = "<b>{point.name}</b><br>
                   <b>{point.y}</b> ({point.percentage:.1f}%)"
  ) %>%
  hc_legend(
    itemStyle = list(
      fontWeight = "bold",
      fontSize = "14px"
    )
  )

```
### NO. OF ELIGABLE FARMERS BY GENDER  {data-width=500}

```{r}
library(dplyr)
library(highcharter)

dataps %>% 
  mutate(
    split_group = recode(
      as.character(split_group),
      "1" = "Group A",
      "2" = "Group B",
      "3" = "Group C"
    )
  ) %>% 
  count(split_group) %>% 
  hchart(
    type = "pie",
    hcaes(
      x = split_group,
      y = n,
      color = split_group
    ),
    colors = group_colors
  ) %>% 
  hc_title(
    text = "Split Group Composition",
    style = list(
      fontWeight = "bold",
      fontSize = "20px"
    )
  ) %>%
  hc_plotOptions(
    pie = list(
      innerSize = "60%",
      dataLabels = list(
        enabled = TRUE,
        useHTML = TRUE,
        style = list(
          fontWeight = "bold",
          fontSize = "14px"
        ),
        format = "<b>{point.name}</b><br>{point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_tooltip(
    useHTML = TRUE,
    style = list(
      fontWeight = "bold",
      fontSize = "14px"
    ),
    pointFormat = "<b>{point.name}</b><br>
                   <b>{point.y}</b> ({point.percentage:.1f}%)"
  ) %>%
  hc_legend(
    itemStyle = list(
      fontWeight = "bold",
      fontSize = "14px"
    )
  )
```

## Column

### TOTAL NO. OF SYNCED PHONE SURVEY INTERVIEWS BY REGION {data-width=600}

```{r }
library(dplyr)
library(highcharter)

dataps %>% 
  count(region) %>%
  arrange(desc(n)) %>% 
  mutate(
    region = factor(region, levels = region),
    name = region,
    y = n
  ) %>%
  hchart(
    type = "bar",
    hcaes(x = name, y = y),
    colorByPoint = TRUE
  ) %>%
  hc_title(
    text = "Number of Records by Region",
    style = list(fontWeight = "bold", fontSize = "18px")
  ) %>%
  hc_xAxis(
    title = list(
      text = "Region",
      style = list(fontWeight = "bold")
    ),
    labels = list(
      style = list(fontWeight = "bold", fontSize = "12px")
    )
  ) %>%
  hc_yAxis(
    title = list(
      text = "Total Count",
      style = list(fontWeight = "bold")
    ),
    labels = list(
      style = list(fontWeight = "bold")
    )
  ) %>%
  hc_plotOptions(
    bar = list(
      pointWidth = 22,  
      dataLabels = list(
        enabled = TRUE,
        style = list(
          fontWeight = "bold",
          fontSize = "12px"
        )
      )
    )
  ) %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> records"
  ) %>%
  hc_colors(c(
    "#1ABC9C", "#3498DB", "#9B59B6", "#F39C12",
    "#E74C3C", "#2ECC71", "#34495E", "#E91E63"
  ))
```

MORE GRAPH ON PHONE SURVEY
=====================================
Row
-----------------------------------------------------------------------

### ATA PHONE SURVEY RESPONDENT'S HOTLINE AWARENESS {data-width=400}

```{r }
dataps %>% 
  dplyr::filter(!is.na(q2_4_a)) %>% 
  dplyr::count(q2_4_a) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    "pie",
    hcaes(
      x = q2_4_a,
      y = n
    )
  ) %>%
  hc_title(text = "Have you ever heard of the 8028 Farmer Hotline?") %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> respondents<br>{point.percentage:.1f}%"
  ) %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_colors(c("#2ECC71", "#E74C3C"))


```


### NO. OF SYNCED PHONE INTERVIEWS BY AGE GROUP  {data-width=400}

```{r }
library(dplyr)
library(highcharter)

dataps %>%
  filter(!is.na(age)) %>%
  mutate(
    age = as.numeric(age),
    age_group = cut(
      age,
      breaks = c(15, 24, 34, 44, 54, 64, Inf),
      labels = c("15–24", "25–34", "35–44", "45–54", "55–64", "65+")
    )
  ) %>%
  count(age_group) %>%
  hchart(
    "pie",
    hcaes(x = age_group, y = n)
  ) %>%
  hc_title(text = "Respondents by Age Group") %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.percentage:.1f}%"
      )
    )
  ) %>%
  hc_colors(c("#2E7D32", "#F9A825", "#EC407A", "#21E1E1", "#FF9800", "#9E9E9E"))


```

### ATA PHONE SURVEY REPORT BY MAIN MOBILE USER {data-width=400}

```{r }
dataps %>% 
  dplyr::filter(!is.na(q1_2_a)) %>% 
  dplyr::count(q1_2_a) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    "pie",
    hcaes(
      x = q1_2_a,
      y = n
    )
  ) %>%
  hc_title(text = "Are you the main user of this mobile phone number?") %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> respondents<br>{point.percentage:.1f}%"
  ) %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_colors(c("#2ECC71", "#E91ED3"))

```

Column 
-----------------------------------------------------------------------

### ATA PHONE SURVEY RESPONDENT'S EDUCATIONAL STATUSE OF RESPONDENTS {data-width=400}

```{r }
dataps %>% 
  filter(!is.na(q2_1_i)) %>%
  count(q2_1_i) %>%
  arrange(desc(n)) %>% 
  hchart(
    "column",
    hcaes(x = q2_1_i, y = n)
  ) %>%
  hc_title(text = "Education Status of Respondents") %>%
  hc_xAxis(title = list(text = "Attended School")) %>%
  hc_yAxis(title = list(text = "Number of Respondents")) %>%
  hc_plotOptions(
    column = list(
      borderRadius = 6,
      dataLabels = list(
        enabled = TRUE,
        format = "{point.y}",
        style = list(fontWeight = "bold")
      )
    )
  )

```

### NO. OF SYNCED PHONE SURVEY INTERVIEWS BY DATE {data-width=300}

```{r}
library(dplyr)
library(highcharter)

dataps %>%
  mutate(
    SubmissionDate = as.Date(SubmissionDate, format = "%d%b%Y")
  ) %>%
  count(SubmissionDate) %>%
  arrange(SubmissionDate) %>%
  hchart(
    "line",
    hcaes(
      x = datetime_to_timestamp(SubmissionDate),
      y = n
    )
  ) %>%
  hc_title(text = "Interviews Over Interview Submission Date") %>%
  hc_xAxis(type = "datetime", title = list(text = "Submission Date")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_colors("#2E7D32")

```


### ATA PHONE SURVEY INTERVIEW LANGUAGE {data-width=400}
```{r}
library(dplyr)
library(highcharter)

dataps %>% 
  dplyr::filter(!is.na(language)) %>% 
  dplyr::count(language) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    type = "pie",
    hcaes(
      x = language,
      y = n
    )
  ) %>%
  hc_title(
    text = "Language Interview Conducted With",
    align = "center",
    style = list(fontSize = "18px", fontWeight = "bold")
  ) %>%
  hc_subtitle(
    text = "Phone Survey Respondents",
    align = "center"
  ) %>%
  hc_plotOptions(
    pie = list(
      innerSize = "60%",          # Donut style
      borderWidth = 1,
      borderColor = "#FFFFFF",
      dataLabels = list(
        enabled = TRUE,
        distance = 15,
        format = "<b>{point.name}</b><br>{point.y} ({point.percentage:.1f}%)",
        style = list(fontSize = "12px")
      )
    )
  ) %>%
  hc_tooltip(
    backgroundColor = "#FFFFFF",
    borderColor = "#CCCCCC",
    pointFormat = "<b>{point.name}</b><br>
                   Respondents: <b>{point.y}</b><br>
                   Percentage: <b>{point.percentage:.1f}%</b>"
  ) %>%
  hc_legend(
    align = "right",
    verticalAlign = "middle",
    layout = "vertical"
  ) %>%
  hc_colors(
    c("#1F77B4", "#FF7F0E", "#2CA02C", "#9467BD", "#8C564B")
  )
```