---
title: "WB Farmer Hotline Screening Phone Survey"
author: "Frontieri consultancy"

date: "[Feb 21, 2026 | 08:00 AM]"

output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: fill
    
    logo: logo.png
    
---


```{r setup, include=FALSE}
library(flexdashboard)
library(haven)
library(plyr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(highcharter)
library(plotly)
library(DT)
library(stringr)
library(ggplot2)
library(viridis)
library(hrbrthemes)
```
```{r}
#Phone Survey
dataps <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/ATI_Farmer_Hotline_phone_survey_500_Callers_WIDE.dta"
)

dataps <- dataps %>% mutate(across(where(is.labelled), as_factor))

dataps <- dataps %>%
  rename(
    region        = region_preload,
    supervisor_name = supervisor,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

dataps <- dataps %>%
  mutate(
    supervisor_name = str_replace_all(
      supervisor_name,
      c(
        "Shambel Awgachew" = "Shambel",
        "Jemila Umar" = "Jemila",
        "Fikiru Yigezu" = "Fikiru",
        "Gachano Gemechu" = "Gachano",
        "Gashayeneh Deribe" = "Gashayeneh",
        "Misrak Birhanu" = "Misrak"
      )
    )
  )

```

```{r}
#Backcheck Survey
databc <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/Back_Check_Survey_500_Callers_WIDE.dta"
)

databc <- databc %>% mutate(across(where(is.labelled), as_factor))

databc <- databc %>%
  rename(
    region        = region_preload,
    supervisor_name = supervisor,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

databc <- databc %>%
  mutate(
    supervisor_name = str_replace_all(
      supervisor_name,
      c(
        "Shambel Awgachew" = "Shambel",
        "Jemila Umar" = "Jemila",
        "Fikiru Yigezu" = "Fikiru",
        "Gachano Gemechu" = "Gachano",
        "Gashayeneh Deribe" = "Gashayeneh",
        "Misrak Birhanu" = "Misrak"
      )
    )
  )
  
```

```{r}
#Pilot Survey
datapis <- read_dta(
  "D:/Econsight/Dashboard/WB Farmer Hotline Screening Phone_Survey/Raw Data/Pilot_Farmer_Hotline_Screening_Phone_Survey_WIDE.dta"
)

datapis <- datapis %>% mutate(across(where(is.labelled), as_factor))

datapis <- datapis %>%
  rename(
    region        = region_preload,
    enum_name     = enumerator_name,
    marital_statu = q1_2_d
  ) %>%
  select(-consent) %>%
  rename(consent = consent1)

datapis <- datapis %>%
  mutate(
    enum_name = str_replace_all(
      enum_name,
      c(
        "Abidulahi mohammed" = "Abidulahi",
        "Addis Worku" = "Addis",
        "Aklilu Zewde Birhane" = "Aklilu",
        "Atakilit Tadesse" = "Atakilit",
        "Bruktawit Molla" = "Bruktawit",
        "Daniel Abebaw" = "Daniel",
        "Eyerus halfom" = "Eyerus",
        "Hilariy Girmay" = "Hilariy",
        "Kabtamu Alemayehu" = "Kabtamu",
        "Kalkidan Wondatir" = "Kalkidan",
        "Mariyam Gudeta" = "Mariyam",
        "Ruth Asfaw" = "Ruth",
        "Shewakena Damitew" = "Shewakena",
        "Sitota G/melak" = "Sitota",
        "Tadele Ejo" = "Tadele",
        "Tena tesfaye" = "Tena",
        "Tirsit Seyoum" = "Tirsit",
        "Tirunesh Ajema" = "Tirunesh",
        "Urgessa Mekonnen" = "Urgessa",
        "Fikadu Thomas" = "Fikadu",
        "Yakob Debela" = "Yakob"
      )
    )
  )

```

ATA PHONE SURVEY
=====================================
Row
-----------------------------------------------------------------------


### TOTAL SYNCED ATA PHONE SURVEY INTERVIEWS

```{r}
total_interview<-nrow(dataps)
valueBox(total_interview, icon = "fa-bar-chart")
```

### TOTAL SYNCED ATA PILOT INTERVIEWS

```{r}
total_interview<-nrow(datapis)
valueBox(total_interview, icon = "fa-bar-chart")
```

### TOTAL SYNCED ATA BACKCHECK INTERVIEWS

```{r}
total_interview<-nrow(databc)
valueBox(total_interview, icon = "fa-bar-chart")
```

## Column

### NO. OF SYNCED PHONE INTERVIEWS BY SUPERVISORS {data-width="600"}

```{r }
library(dplyr)
library(highcharter)

dataps %>% 
  filter(!is.na(supervisor_name)) %>% 
  count(supervisor_name) %>% 
  arrange(desc(n)) %>% 
  mutate(
    name = supervisor_name,
    y = n
  ) %>% 
  hchart(
    type = "column",
    hcaes(x = name, y = y),
    colorByPoint = TRUE
  ) %>%
  hc_title(text = "Number of Interviews Synced by Teams") %>%
  hc_xAxis(
    title = list(text = "Supervisors"),
    labels = list(rotation = -20)
  ) %>%
  hc_yAxis(
    title = list(text = "Total Interviews Synced")
  ) %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> interviews"
  ) %>%
  hc_plotOptions(
    column = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.y}"
      ),
      states = list(
        hover = list(
          brightness = 0.25 
        )
      )
    )
  ) %>%
  hc_colors(c(
    "#2ECC71", "#3498DB", "#F1C40F", "#E67E22",
    "#9B59B6", "#1ABC9C", "#E91E63", "#34495E"
  ))

```


### NO. OF SYNCED PHONE SURVEY INTERVIEWS BY SPLIT GROUP {data-width=400}

```{r }
library(dplyr)
library(highcharter)

dataps %>% 
  mutate(
    split_group = recode(
      as.character(split_group),
      "1" = "Group A",
      "2" = "Group B",
      "3" = "Group C"
    )
  ) %>% 
  count(split_group) %>% 
  hchart(
    type = "pie",
    hcaes(
      x = split_group,
      y = n,
      color = split_group
    ),
    colors = group_colors
  ) %>% 
  hc_plotOptions(
    pie = list(
      innerSize = "60%",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b><br>{point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>% 
  hc_title(text = "Split Group Composition")

```
### TOTAL NO. OF SYNCED PHONE SURVEY INTERVIEWS BY REGION {data-width=600}

```{r }
dataps %>% 
  dplyr::count(region) %>%
  arrange(-n) %>% 
  hchart('bar', hcaes(x = 'region', y = 'n'), color_stops(n=4, colors = c("#F65A83", "#FF1E00", "#21E1E1", "#224B0C")))
```

## Column

### NO. OF SYNCED PHONE SURVEY INTERVIEWS BY GENDER {data-width=300}

```{r }
dataps %>% 
  filter(!is.na(gender)) %>%
  count(gender) %>%
  mutate(
    percent = n / sum(n) * 100
  ) %>%
  hchart(
    "pie",
    hcaes(x = gender, y = n)
  ) %>%
  hc_plotOptions(
    pie = list(
      innerSize = "55%",
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.y} ({point.percentage:.1f}%)",
        style = list(fontWeight = "bold", fontSize = "12px")
      )
    )
  ) %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> interviews<br>{point.percentage:.1f}%"
  ) %>%
  hc_colors(
    c(
      "Male"   = "#2E7D32", 
      "Female" = "#EC407A"
    )
  )
```

### NO. OF SYNCED PHONE SURVEY  {data-width=500}

```{r}

dataps %>% 
  dplyr::select(study1, study2, study3) %>%
  
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "study",
    values_to = "value"
  ) %>%
  
  dplyr::filter(value %in% c(0, 1)) %>%
  
  dplyr::count(study, value) %>%
  
  dplyr::group_by(study) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  dplyr::ungroup() %>%
  
  # plot
  hchart(
    type = "column",
    hcaes(
      x = study,
      y = n,
      group = factor(value)
    )
  ) %>%
  
  hc_title(
    text = "Distribution of Study Variables",
    align = "center",
    style = list(fontSize = "18px", fontWeight = "bold")
  ) %>%
  
  hc_plotOptions(
    column = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.y} ({point.percentage:.1f}%)",
        style = list(fontSize = "11px")
      )
    )
  ) %>%
  
  hc_tooltip(
    pointFormat = "<b>{series.name}</b><br>
                   Count: <b>{point.y}</b><br>
                   Percentage: <b>{point.percentage:.1f}%</b>"
  ) %>%
  
  hc_legend(
    title = list(text = "Value (0 = No, 1 = Yes)"),
    align = "right",
    verticalAlign = "middle"
  ) %>%
  
  hc_colors(c("#D62728", "#2CA02C"))
```

### NO. OF SYNCED PHONE SURVEY  {data-width=500}

```{r }
library(dplyr)
library(tidyr)
library(highcharter)

dataps %>% 
  select(gender, study1, study2, study3) %>%
  filter(!is.na(gender)) %>%
  
  pivot_longer(
    cols = c(study1, study2, study3),
    names_to = "study",
    values_to = "value"
  ) %>%
  
  filter(value %in% c(0, 1)) %>%
  
  count(study, gender, value) %>%
  
  group_by(study, gender) %>%
  mutate(percent = round(n / sum(n) * 100, 1)) %>%
  ungroup() %>%
  
  hchart(
    type = "column",
    hcaes(
      x = study,
      y = n,
      group = interaction(gender, value)
    )
  ) %>%
  
  hc_chart(
    height = 500,
    backgroundColor = "#FAFAFA"
  ) %>%
  
  hc_colors(c("#4E79A7", "#A0CBE8", "#F28E2B", "#FFBE7D")) %>%
  
  hc_title(
    text = "Distribution of Study Variables by Gender",
    align = "center",
    style = list(fontSize = "18px", fontWeight = "bold")
  ) %>%
  
  hc_subtitle(
    text = "Stacked bars: 0 = No, 1 = Yes",
    align = "center"
  ) %>%
  
  hc_plotOptions(
    column = list(
      stacking = "normal",
      borderWidth = 0,
      pointPadding = 0.08,
      groupPadding = 0.2,
      dataLabels = list(
        enabled = TRUE,
        format = "{point.y}",
        style = list(
          fontSize = "11px",
          fontWeight = "bold",
          textOutline = "none"
        )
      )
    )
  ) %>%
  
  hc_tooltip(
    useHTML = TRUE,
    backgroundColor = "#FFFFFF",
    borderColor = "#CCCCCC",
    pointFormat = "
      <b>{series.name}</b><br>
      Count: <b>{point.y}</b>
    "
  ) %>%
  
  hc_legend(
    layout = "vertical",
    align = "right",
    verticalAlign = "middle",
    symbolRadius = 0,
    itemStyle = list(fontSize = "12px")
  )

```

MORE GRAPH ON PHONE SURVEY
=====================================
Row
-----------------------------------------------------------------------

### ATA PHONE SURVEY RESPONDENT'S HOTLINE AWARENESS {data-width=400}

```{r }
dataps %>% 
  dplyr::filter(!is.na(q2_4_a)) %>% 
  dplyr::count(q2_4_a) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    "pie",
    hcaes(
      x = q2_4_a,
      y = n
    )
  ) %>%
  hc_title(text = "Have you ever heard of the 8028 Farmer Hotline?") %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> respondents<br>{point.percentage:.1f}%"
  ) %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_colors(c("#2ECC71", "#E74C3C"))


```


### NO. OF SYNCED PHONE INTERVIEWS BY AGE GROUP  {data-width=400}

```{r }
library(dplyr)
library(highcharter)

dataps %>%
  filter(!is.na(age)) %>%
  mutate(
    age = as.numeric(age),
    age_group = cut(
      age,
      breaks = c(15, 24, 34, 44, 54, 64, Inf),
      labels = c("15–24", "25–34", "35–44", "45–54", "55–64", "65+")
    )
  ) %>%
  count(age_group) %>%
  hchart(
    "pie",
    hcaes(x = age_group, y = n)
  ) %>%
  hc_title(text = "Respondents by Age Group") %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.percentage:.1f}%"
      )
    )
  ) %>%
  hc_colors(c("#2E7D32", "#F9A825", "#EC407A", "#21E1E1", "#FF9800", "#9E9E9E"))


```

### ATA PHONE SURVEY REPORT BY MAIN MOBILE USER {data-width=400}

```{r }
dataps %>% 
  dplyr::filter(!is.na(q1_2_a)) %>% 
  dplyr::count(q1_2_a) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    "pie",
    hcaes(
      x = q1_2_a,
      y = n
    )
  ) %>%
  hc_title(text = "Are you the main user of this mobile phone number?") %>%
  hc_tooltip(
    pointFormat = "<b>{point.y}</b> respondents<br>{point.percentage:.1f}%"
  ) %>%
  hc_plotOptions(
    pie = list(
      dataLabels = list(
        enabled = TRUE,
        format = "{point.name}: {point.y} ({point.percentage:.1f}%)"
      )
    )
  ) %>%
  hc_colors(c("#2ECC71", "#E91ED3"))

```

Column 
-----------------------------------------------------------------------

### ATA PHONE SURVEY RESPONDENT'S EDUCATIONAL STATUSE OF RESPONDENTS {data-width=400}

```{r }
dataps %>% 
  filter(!is.na(q2_1_i)) %>%
  count(q2_1_i) %>%
  arrange(desc(n)) %>% 
  hchart(
    "column",
    hcaes(x = q2_1_i, y = n)
  ) %>%
  hc_title(text = "Education Status of Respondents") %>%
  hc_xAxis(title = list(text = "Attended School")) %>%
  hc_yAxis(title = list(text = "Number of Respondents")) %>%
  hc_plotOptions(
    column = list(
      borderRadius = 6,
      dataLabels = list(
        enabled = TRUE,
        format = "{point.y}",
        style = list(fontWeight = "bold")
      )
    )
  )

```

### NO. OF SYNCED PHONE SURVEY INTERVIEWS BY DATE {data-width=300}

```{r}
library(dplyr)
library(highcharter)

dataps %>%
  mutate(
    SubmissionDate = as.Date(SubmissionDate, format = "%d%b%Y")
  ) %>%
  count(SubmissionDate) %>%
  arrange(SubmissionDate) %>%
  hchart(
    "line",
    hcaes(
      x = datetime_to_timestamp(SubmissionDate),
      y = n
    )
  ) %>%
  hc_title(text = "Interviews Over Interview Submission Date") %>%
  hc_xAxis(type = "datetime", title = list(text = "Submission Date")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_colors("#2E7D32")

```


### ATA PHONE SURVEY INTERVIEW LANGUAGE {data-width=400}
```{r}
library(dplyr)
library(highcharter)

dataps %>% 
  dplyr::filter(!is.na(language)) %>% 
  dplyr::count(language) %>%
  dplyr::mutate(
    percent = round(n / sum(n) * 100, 1),
    label = paste0(n, " (", percent, "%)")
  ) %>%
  hchart(
    type = "pie",
    hcaes(
      x = language,
      y = n
    )
  ) %>%
  hc_title(
    text = "Language Interview Conducted With",
    align = "center",
    style = list(fontSize = "18px", fontWeight = "bold")
  ) %>%
  hc_subtitle(
    text = "Phone Survey Respondents",
    align = "center"
  ) %>%
  hc_plotOptions(
    pie = list(
      innerSize = "60%",          # Donut style
      borderWidth = 1,
      borderColor = "#FFFFFF",
      dataLabels = list(
        enabled = TRUE,
        distance = 15,
        format = "<b>{point.name}</b><br>{point.y} ({point.percentage:.1f}%)",
        style = list(fontSize = "12px")
      )
    )
  ) %>%
  hc_tooltip(
    backgroundColor = "#FFFFFF",
    borderColor = "#CCCCCC",
    pointFormat = "<b>{point.name}</b><br>
                   Respondents: <b>{point.y}</b><br>
                   Percentage: <b>{point.percentage:.1f}%</b>"
  ) %>%
  hc_legend(
    align = "right",
    verticalAlign = "middle",
    layout = "vertical"
  ) %>%
  hc_colors(
    c("#1F77B4", "#FF7F0E", "#2CA02C", "#9467BD", "#8C564B")
  )
```